Preparing Future Technical Writing Teachers

### 2019-03-13 futurefaculty.Rmd
update

---
title: "Preparing Future Technical Writing Teachers"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
---

@@

Even when faculty are motivated to innovate, how they learn about alternative strategies affects the odds of adoption. For example, faculty who attend formal professional development activities that promote evidence- based practices are less likely to adopt those practices than if they learn about them from trusted colleagues or respected opinion leaders [@Andrews2016]. In contrast, graduate students who participate in formal professional development about learner-centered instruction readily adopt learner-centered methods into their personal teaching practice [(]@Ebert-May2015]. A more effective strategy for changing faculty instructional practices may be to target and train future faculty who then act as change agents [@Tanner2006].

####\  
***

>>>>

---
title: "Preparing Future Technical Writing Teachers"
date: "`r format(Sys.time(), '%b %d, %Y')`"
bibliography: library.bib
biblio-style: apalike
nocite: | 
  @Nilson2014
---

@@

Even when faculty are motivated to innovate, how they learn about alternative strategies affects the odds of adoption. For example, faculty who attend formal professional development activities that promote evidence- based practices are less likely to adopt those practices than if they learn about them from trusted colleagues or respected opinion leaders [@Andrews2016]. In contrast, graduate students who participate in formal professional development about learner-centered instruction readily adopt learner-centered methods into their personal teaching practice [@Ebert-May2015]. A more effective strategy for changing faculty instructional practices may be to target and train future faculty who then act as change agents [@Tanner2006].

####\  
***
*Works Cited*
